How do changes in ex vary between countries?

### 2022-03-15 draft_working_paper.Rmd

  ex_ENW <- hmd_ex_selected_countries_with_synth %>%
      filter(sex %in% c("female", "male")) %>%
      filter(code == "GBRTENW") %>%
    group_by(sex, x) %>% arrange(year) %>%
      mutate(delta_ex = ex - lag(ex)) %>%
    ungroup %>%
    filter(year >= 1979) %>%
    ggplot(aes(x = year, y = delta_ex)) + geom_point() +
   geom_line() +
   geom_hline(yintercept = 0) +
    stat_smooth(mapping = aes(colour = sex)) +
       facet_grid(x ~ sex)

@@

 ex_SCO <- hmd_ex_selected_countries_with_synth %>%
      filter(sex %in% c("female", "male")) %>%
      filter(code == "GBR_SCO") %>%
    group_by(sex, x) %>% arrange(year) %>%
      mutate(delta_ex = ex - lag(ex)) %>%
    ungroup %>%
    filter(year >= 1979) %>%
    ggplot(aes(x = year, y = delta_ex)) + geom_point() +
   geom_line() +
   geom_hline(yintercept = 0) +
    stat_smooth(mapping = aes(colour = sex)) +
       facet_grid(x ~ sex)

@@

 ex_FRA <- hmd_ex_selected_countries_with_synth %>%
      filter(sex %in% c("female", "male")) %>%
      filter(code == "FRATNP") %>%
    group_by(sex, x) %>% arrange(year) %>%
      mutate(delta_ex = ex - lag(ex)) %>%
    ungroup %>%
    filter(year >= 1979) %>%
    ggplot(aes(x = year, y = delta_ex)) + geom_point() +
   geom_line() +
   geom_hline(yintercept = 0) +
    stat_smooth(mapping = aes(colour = sex)) +
       facet_grid(x ~ sex)

@@

 ex_ESP <- hmd_ex_selected_countries_with_synth %>%
      filter(sex %in% c("female", "male")) %>%
      filter(code == "ESP") %>%
    group_by(sex, x) %>% arrange(year) %>%
      mutate(delta_ex = ex - lag(ex)) %>%
    ungroup %>%
    filter(year >= 1979) %>%
    ggplot(aes(x = year, y = delta_ex)) + geom_point() +
   geom_line() +
   geom_hline(yintercept = 0) +
    stat_smooth(mapping = aes(colour = sex)) +
       facet_grid(x ~ sex)

@@

 ex_ITA <- hmd_ex_selected_countries_with_synth %>%
      filter(sex %in% c("female", "male")) %>%
      filter(code == "ITA") %>%
    group_by(sex, x) %>% arrange(year) %>%
      mutate(delta_ex = ex - lag(ex)) %>%
    ungroup %>%
    filter(year >= 1979) %>%
    ggplot(aes(x = year, y = delta_ex)) + geom_point() +
   geom_line() +
   geom_hline(yintercept = 0) +
    stat_smooth(mapping = aes(colour = sex)) +
       facet_grid(x ~ sex)

@@

 #Grid
 ex_DEUTSYNTH <- hmd_ex_selected_countries_with_synth %>%
      filter(sex %in% c("female", "male")) %>%
      filter(code == "DEUTSYNTH") %>%
    group_by(sex, x) %>% arrange(year) %>%
      mutate(delta_ex = ex - lag(ex)) %>%
    ungroup %>%
    filter(year >= 1979) %>%
    ggplot(aes(x = year, y = delta_ex)) + geom_point() +
   geom_line() +
   geom_hline(yintercept = 0) +
    stat_smooth(mapping = aes(colour = sex)) +
       facet_grid(x ~ sex)

@@

 ex_DEUTE <- hmd_ex_selected_countries_with_synth %>%
      filter(sex %in% c("female", "male")) %>%
      filter(code == "DEUTE") %>%
    group_by(sex, x) %>% arrange(year) %>%
      mutate(delta_ex = ex - lag(ex)) %>%
    ungroup %>%
    filter(year >= 1979) %>%
    ggplot(aes(x = year, y = delta_ex)) + geom_point() +
   geom_line() +
   geom_hline(yintercept = 0) +
    stat_smooth(mapping = aes(colour = sex)) +
       facet_grid(x ~ sex)

@@

 ex_DEUTW <- hmd_ex_selected_countries_with_synth %>%
      filter(sex %in% c("female", "male")) %>%
      filter(code == "DEUTW") %>%
    group_by(sex, x) %>% arrange(year) %>%
      mutate(delta_ex = ex - lag(ex)) %>%
    ungroup %>%
    filter(year >= 1979) %>%
    ggplot(aes(x = year, y = delta_ex)) + geom_point() +
   geom_line() +
   geom_hline(yintercept = 0) +
    stat_smooth(mapping = aes(colour = sex)) +
       facet_grid(x ~ sex)

>>>>

  ex_ENW <- hmd_ex_selected_countries_with_synth %>%
      filter(sex %in% c("female", "male")) %>%
      filter(code == "GBRTENW") %>%
    group_by(sex, x) %>% arrange(year) %>%
      mutate(delta_ex = ex - lag(ex)) %>%
    ungroup %>%
    filter(year >= 1979) %>%
    ggplot(aes(x = year, y = delta_ex)) + geom_point(size=0.3) +
   geom_line() +
   geom_hline(yintercept = 0) +
    stat_smooth(mapping = aes(colour = sex)) +
       facet_grid(x ~ sex)

@@

 ex_SCO <- hmd_ex_selected_countries_with_synth %>%
      filter(sex %in% c("female", "male")) %>%
      filter(code == "GBR_SCO") %>%
    group_by(sex, x) %>% arrange(year) %>%
      mutate(delta_ex = ex - lag(ex)) %>%
    ungroup %>%
    filter(year >= 1979) %>%
    ggplot(aes(x = year, y = delta_ex)) + geom_point(size=0.3) +
   geom_line() +
   geom_hline(yintercept = 0) +
    stat_smooth(mapping = aes(colour = sex)) +
       facet_grid(x ~ sex)

@@

 ex_FRA <- hmd_ex_selected_countries_with_synth %>%
      filter(sex %in% c("female", "male")) %>%
      filter(code == "FRATNP") %>%
    group_by(sex, x) %>% arrange(year) %>%
      mutate(delta_ex = ex - lag(ex)) %>%
    ungroup %>%
    filter(year >= 1979) %>%
    ggplot(aes(x = year, y = delta_ex)) + geom_point(size=0.3) +
   geom_line() +
   geom_hline(yintercept = 0) +
    stat_smooth(mapping = aes(colour = sex)) +
       facet_grid(x ~ sex)

@@

 ex_ESP <- hmd_ex_selected_countries_with_synth %>%
      filter(sex %in% c("female", "male")) %>%
      filter(code == "ESP") %>%
    group_by(sex, x) %>% arrange(year) %>%
      mutate(delta_ex = ex - lag(ex)) %>%
    ungroup %>%
    filter(year >= 1979) %>%
    ggplot(aes(x = year, y = delta_ex)) + geom_point(size=0.3) +
   geom_line() +
   geom_hline(yintercept = 0) +
    stat_smooth(mapping = aes(colour = sex)) +
       facet_grid(x ~ sex)

@@

 ex_ITA <- hmd_ex_selected_countries_with_synth %>%
      filter(sex %in% c("female", "male")) %>%
      filter(code == "ITA") %>%
    group_by(sex, x) %>% arrange(year) %>%
      mutate(delta_ex = ex - lag(ex)) %>%
    ungroup %>%
    filter(year >= 1979) %>%
    ggplot(aes(x = year, y = delta_ex)) + geom_point(size=0.3) +
   geom_line() +
   geom_hline(yintercept = 0) +
    stat_smooth(mapping = aes(colour = sex)) +
       facet_grid(x ~ sex)

@@

 #Grid
 ex_DEUTSYNTH <- hmd_ex_selected_countries_with_synth %>%
      filter(sex %in% c("female", "male")) %>%
      filter(code == "DEUTSYNTH") %>%
    group_by(sex, x) %>% arrange(year) %>%
      mutate(delta_ex = ex - lag(ex)) %>%
    ungroup %>%
    filter(year >= 1979) %>%
    ggplot(aes(x = year, y = delta_ex)) + geom_point(size=0.3) +
   geom_line() +
   geom_hline(yintercept = 0) +
    stat_smooth(mapping = aes(colour = sex)) +
       facet_grid(x ~ sex)

@@

 ex_DEUTE <- hmd_ex_selected_countries_with_synth %>%
      filter(sex %in% c("female", "male")) %>%
      filter(code == "DEUTE") %>%
    group_by(sex, x) %>% arrange(year) %>%
      mutate(delta_ex = ex - lag(ex)) %>%
    ungroup %>%
    filter(year >= 1979) %>%
    ggplot(aes(x = year, y = delta_ex)) + geom_point(size=0.3) +
   geom_line() +
   geom_hline(yintercept = 0) +
    stat_smooth(mapping = aes(colour = sex)) +
       facet_grid(x ~ sex)

@@

 ex_DEUTW <- hmd_ex_selected_countries_with_synth %>%
      filter(sex %in% c("female", "male")) %>%
      filter(code == "DEUTW") %>%
    group_by(sex, x) %>% arrange(year) %>%
      mutate(delta_ex = ex - lag(ex)) %>%
    ungroup %>%
    filter(year >= 1979) %>%
    ggplot(aes(x = year, y = delta_ex)) + geom_point(size=0.3) +
   geom_line() +
   geom_hline(yintercept = 0) +
    stat_smooth(mapping = aes(colour = sex)) +
       facet_grid(x ~ sex)
